\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Informe Final}

### 2016-05-27 article.tex
Reorganiced code

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

\usepackage{titlesec} % Allows customization of titles
\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

@@

\author{
\large
\textsc{Alberto Amigo Alonso\textsubscript{20\%}}\\[2mm] % Your name
\textsc{Sergio Delgado Álvarez\textsubscript{20\%}}\\[2mm] % Your name
\textsc{Sergio García Prado\textsubscript{20\%}}\\[2mm] % Your name
\textsc{Oscar Fernández Angulo\textsubscript{20\%}}\\[2mm] % Your name
\textsc{Silvia Rodriguez Ares\textsubscript{20\%}}\\[2mm] % Your name
\normalsize Universidad de Valladolid \\ % Your institution
\vspace{-5mm}
}
\date{}

@@

\begin{document}

	\maketitle % Insert title

@@

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

	\begin{abstract}
		\noindent Servicio web destinado a permitir a remitentes y destinatarios ofertar envíos para que los transportistas sean capaces de encontrarlos permitiendo a todos los usuarios monitorizarlos.
	\end{abstract}

@@

		\begin{figure}[H]
			\centering
				\includegraphics[width=0.75\textwidth]{sitemap.png}
		\end{figure}

@@

		\begin{figure}[H]
			\centering
				\includegraphics[width=1\textwidth]{database.png}
		\end{figure}
%----------------------------------------------------------------------------------------
%	Bibliographic references
%----------------------------------------------------------------------------------------
	\begin{thebibliography}{9}

>>>>

@@

\author{
\large
\textsc{Alberto Amigo Alonso\textsubscript{20\%}}\\[2mm] % Your name
\textsc{Sergio Delgado Álvarez\textsubscript{20\%}}\\[2mm] % Your name
\textsc{Sergio García Prado\textsubscript{20\%}}\\[2mm] % Your name
\textsc{Oscar Fernández Angulo\textsubscript{20\%}}\\[2mm] % Your name
\textsc{Silvia Rodriguez Ares\textsubscript{20\%}}\\[2mm] % Your name
\normalsize Universidad de Valladolid \\ % Your institution
\vspace{-5mm}
}
\date{Mayo 2016}

@@

\begin{document}
	\begin{titlepage}
	\centering
		%\includegraphics[width=0.15\textwidth]{example-image-1x1}\par\vspace{1cm}
		{\scshape\LARGE Universidad de Valladolid \par}
		\vspace{1cm}
		{\scshape\Large Informe Final\par}
		\vspace{1.5cm}
		{\huge\bfseries JumpVa\par}
		\vspace{2cm}
		{\large
		\textsc{Alberto Amigo Alonso\textsubscript{20\%}}\\[2mm] % Your name
		\textsc{Sergio Delgado Álvarez\textsubscript{20\%}}\\[2mm] % Your name
		\textsc{Sergio García Prado\textsubscript{20\%}}\\[2mm] % Your name
		\textsc{Oscar Fernández Angulo\textsubscript{20\%}}\\[2mm] % Your name
		\textsc{Silvia Rodriguez Ares\textsubscript{20\%}}\\[2mm] % Your name
		\vspace{-5mm}
		}
		\vfill
		Servicio web destinado a permitir a remitentes y destinatarios ofertar envíos para que los transportistas sean capaces de encontrarlos permitiendo a todos los usuarios monitorizarlos

		\vfill

	% Bottom of the page
		{\large \today\par}
	\end{titlepage}

@@

%----------------------------------------------------------------------------------------
%	TABLE OF CONTENTS
%----------------------------------------------------------------------------------------

	\tableofcontents
	\newpage

@@

		\begin{figure}[H]
			\centering
				\includegraphics[width=0.75\textwidth]{res/sitemap.png}
		\end{figure}

@@

		\begin{figure}[H]
			\centering
				\includegraphics[width=1\textwidth]{res/database.png}
		\end{figure}
%----------------------------------------------------------------------------------------
%	Bibliographic references
%----------------------------------------------------------------------------------------
	\begin{thebibliography}{9}
